Comprehensive quality - aware Automated Semantic Web Service Composition

### 2016-10-30 paper.tex
update

\title{Comprehensive Quality Awareness Automated Semantic Web Service Composition}

@@

\begin{abstract}
Semantic web service composition has been a prevailing research area in recent years. There are two major governance challenges faced by researchers, one is semantic matchmaking for discovering interoperable web services, which demands a rich “machine understanding” language such as OWL-S (Web Ontology language for Web Services), WSML (Web Service Modeling language, SAWSDL (Semantic Annotations for WSDL and XML Schema). This interaction enables us to pair service functionalities through language understanding and reasoning. Optimisation problems are another challenge, many scholars have looked into the nonfunctional optimisation problems in QoS-awareness web service composition applying AI planning and Evolution Computing techniques. However, it is not sufficient without considering good balance between functional and nonfunctional quality in most scenarios. Therefore, the consideration in these two quality dimensions is a must, so that comprehensive quality  awareness semantic web service composition is proposed to deal with optimisation problems. This paper develops a more applicable approach for measuring comprehensive quality in both semantic matchmaking and QoS optimisation for automated semantic web service composition.
\end{abstract}

\section{Introduction}\label{introduction}
Service-oriented computing (SOC) is a novel computing paradigm that employs services as fundamental elements to achieve agile development of cost-efficient and integratable enterprise applications in heterogeneous environments \cite{papazoglou2003service}. Service Oriented Architecture (SOA) could abstractly realise service-oriented paradigm of computing, this accomplishment has been contributing to reuse of software components, from functions to units, and from units to services during the development in SOA \cite{booth2004web}. One of the most typical realisations of SOA is \textit{web service}, which designated as ``modular, self-describing, self-contained applications that are available on the Internet'' \cite{curbera2001web}. And several standards play a significant role in registering, enquiring and grounding web services, such as UDDI, WSDL and SOAP \cite{fensel2011semantic}.

\textit{Web service composition} pertains to a combination of several web services to provide a value-added composite service that accommodates customers' arbitrarily complex requirements. This application is developed by integrating interoperable and collaborative functionalities over heterogeneous systems --- diverse platforms and programming languages \cite{casati2001technologies}. Due to an increase in a large-scale alignment of enterprise applications, the number of Web services has increased dramatically and unprecedentedly, which cause an immense redundancy in functionality in a huge searching space. Therefore, manual and semi-automated web service composition are considered to be less efficient while automated web service composition is deemed to be less human intervention, less time consumption, and high productivity.

Two most notable challenges for web service composition are ensuring interoperability of services and QoS optimisation \cite{fensel2011semantic}. Interoperability of web services is one challenge in the dimensions of syntactic and semantics \cite{fensel2011semantic}. The syntactic dimension has achieved success through the use of XML standards (such as $WSDL$, $SOAP$), the semantics dimension, on the other hand, demands further research. This semantics given by ontologies \cite{o2005review} enables web service to understand and reason with each other. Historically, there are many ontologies languages and formats for semantic service descriptions, such as OWL-S \cite{martin2004owl}, WSML \cite{fensel2006enabling}, and SAWSDL \cite{lausen2007semantic}, The logical characteristics in reasoning makes ``machine understanding'' possible through identifying and matching semantic similarity in input/output parameters of web services in heterogeneous environments. The second challenge is to find optimised solutions to Quality of Service ($QoS$) over the composite web service. This problems give birth to \textit{QoS-aware service composition} that considers the composition of service-level agreements \cite {sahai2002automated} manifesting a collection of SLA rules and policies for supporting QoS-based composition.

Existing works on service composition are often addressed regarding the above challenges. One group optimises the quality of compositions under a pre-defined abstract workflow, which is considered to be a \textit{semi-automated Web service composition} approach. Another group attempts to generate a composite plan automatically in discovering and selecting suitable web services, which are deemed to be an NP-hard problem \cite{moghaddam2014service}. \textit{Semantic web services composition} is distinguished from the syntactic service composition. Its benefits are presented in eliminating conflicts by the semantic level of web services. In the last few years, substantial work has been done on semantic web service composition \cite{fensel2011semantic,lecue2009optimizing}. However, few works have addressed an automatic semantic web service composition approach, which optimise both QoS and quality of semantic match making as web service composition solutions. For example, customers prefer the highest quality of service solution associated with the acceptable semantic match matching quality.

The overall goal of this paper is to develop an comprehensive quality awareness automated semantic web service composition that satisfactorily optimises both functional and non-functional requirements. Particularly, this project considers a semantic matchmaking quality extension to QoS awareness and two structural constructs (sequence and parallel) for building optimised composition solution using Particle Swarm Optimisation. We aim to provide a more general and applicable way to measure semantic matchmaking in automated semantic web service composition and contribute to the state-of-the-art in this field. Three objectives of this work are accomplished as follows:

\begin{enumerate}
 \item To address semantic matchmaking quality in considering different matching types associated with corresponding semantic similarity, which is demonstrated in a comprehensive quality approach with QoS. This approach is consider to be a more general and applicable way of finding an optimised solution in semantic web service composition.

 \item To apply PSO for implementing comprehensive awareness automated semantic web service composition. PSO sorts out an optimised service queue as a indirect representation of web service composition with consideration of comprehensive quality, and this service queue is further decoded using graph building algorithm to generate a final solution.

 \item To explore the performance of comprehensive quality awareness semantic web service composition, we utilise benchmark datasets from Web Services Challenge 2009 (WSC09) \cite{kona2009wsc}.
\end{enumerate}

The remains of this paper are composed as the following: Sect. \ref{background} provides the knowledge background on the semantic web service composition, including a literature review; Sect. \ref{qswsc_approach} represents the an overview of comprehensive quality awareness semantic automated web service composition consisting of comprehensive quality evaluation model and the whole implementation algorithm; Sect. \ref{experiment_design} describes the experiments conducted to test the effectiveness of proposed model; Sect. \ref{results_analysis} presents the results and analysis of the experiment; Sect. \ref{conclusion} is the paper conclusion.

@@

The purpose of web service composition is to accomplish an arbitrarily complex task fulfilling customer's requirement, which could be denoted as a composite goal: $Comp.G(F(T_{Input}, T_{Output}), NF(T_{QoS}))$. This overall composite goal is demonstrated in two parts. The first functional part is a given task input or input set to get the desired Task output or output set, it typically refers to users' functional requirement; another nonfunctional part specifies the acceptable level of composite quality of service. To accomplish the composite goal, two stages are involved: services discovery and service selection. Firstly, service discovery is to find matched web service: $S_{n}(F(S_{Input}, S_{Output}), NF(S_{QoS}))$ from Service Repository: $S \{S_{1}, S_{2},..., S_{n} \}$ with the given $T_{Input}$. Meanwhile, a output set is initialised and updated with found services output, which could be denoted as  $Output Set(T_{input}, S_{output} \in S_1,...,S_{output} \in S_{n-k})$. The Output Set is used to discovery all related services until the desired $T_{Output}$ found in the updated Output Set. The discovery process normally results in more than one solutions. Service selection is to select one of those composite solution considering the closest QoS to $T_{QoS}$. To ensure the composite solution returns exact the same or very close $T_{Output}$, we consider a comprehensive quality in both discovery and selection stages, where two challenges mentioned in Sect. \ref{introduction} are also addressed in Sect. \ref{qswsc_approach},

>>>>

\title{Comprehensive quality - aware Automated Semantic Web Service Composition}

@@

\begin{abstract}
Semantic web service composition has been a prevailing research area in recent years. There are two major governance challenges faced by researchers. One is semantic matchmaking for discovering interoperable web services, which demands a rich “machine understanding” language such as OWL-S (Web Ontology language for Web Services), WSML (Web Service Modeling language, SAWSDL (Semantic Annotations for WSDL and XML Schema). This interaction of web services enables us to pair service functionalities through understanding and reasoning those semantic descriptions. Optimisation problems are another challenge. Many scholars have looked into nonfunctional optimisation problems in QoS-aware web service composition applying AI planning and Evolution Computing techniques. However, it is not sufficient without considering good balance between functional and nonfunctional quality in most scenarios. Therefore, the consideration in these two quality dimensions is a must, so that service composition needs to deal with optimisation problems in both quality of semantic matchmaking and QoS. This paper develops a more applicable way for measuring a proposed comprehensive quality model in both semantic matchmaking and QoS for automated semantic web service composition.
\end{abstract}

\section{Introduction}\label{introduction}
Service-oriented computing (SOC) is a novel computing paradigm that employs services as fundamental elements to achieve agile development of cost-efficient and integratable enterprise applications in heterogeneous environments \cite{papazoglou2003service}. Service Oriented Architecture (SOA) could abstractly realise service-oriented paradigm of computing. This accomplishment has been contributing to the reuse of software components, from functions to units, and from units to services during the development in SOA \cite{booth2004web}. One of the most typical realisations of SOA is \textit{web service}, which is designated as ``modular, self-describing, self-contained applications that are available on the Internet'' \cite{curbera2001web}. Several standards play a significant role in registering, enquiring and grounding web services including particularly UDDI, WSDL and SOAP \cite{fensel2011semantic}.

\textit{Web service composition} pertains to a combination of multiple web services to provide a value-added composite service that accommodates customers' arbitrarily complex requirements. This application is developed by integrating interoperable and collaborative functionalities over heterogeneous systems. Due to the increase in the number of large-scale enterprise applications, the number of Web services has increased dramatically and unprecedentedly, which cause an immense redundancy in functionality in a huge searching space. Therefore, manual and semi-automated web service composition are considered to be less efficient while automated web service composition is deemed to be less human intervention, less time consumption, and high productivity.

Two most notable challenges for web service composition are $(1)$ ensuring interoperability of services and $(2)$ achieving QoS optimisation \cite{fensel2011semantic}. \textit{Interoperability} of web services presents challenge $(1)$ in the dimensions of syntactic and semantics \cite{fensel2011semantic}. The syntactic dimension is covered the XML-based technologies (such as $WSDL$, $SOAP$). The semantics aspect, on the other hand, demands further research. Through semantics given by ontologies \cite{o2005review}, web services understand and better collaborate with each other. Historically, there are many ontologies languages and formats for semantic service descriptions, such as OWL-S \cite{martin2004owl}, WSML \cite{fensel2006enabling}, and SAWSDL \cite{lausen2007semantic}. The logical characteristics in reasoning makes ``machine understanding'' possible through identifying and matching semantic similarity in input/output parameters of web services in heterogeneous environments. The second challenge $(2)$ is related to finding \textit{optimised solutions} to Quality of Service ($QoS$) over composite web services. This problems give birth to \textit{QoS-aware service composition} that considers the composition of service-level agreements \cite {sahai2002automated} manifesting a collection of SLA rules and policies for supporting QoS-based composition.

Existing works on service composition focus mainly addressing two challenges above. One group optimises the quality of compositions under a pre-defined abstract workflow, which is considered to be a \textit{semi-automated Web service composition} approach. Another group attempts to generate a composite plan automatically in discovering and selecting suitable web services, which are deemed to NP-hard \cite{moghaddam2014service}. \textit{Semantic web services composition} is distinguished from the syntactic service composition. Its benefits are presented in eliminating conflicts by the semantic level of web services. In the past few years, substantial works have been done on semantic web service composition \cite{fensel2011semantic,lecue2009optimizing}. However, few works have enabled truely automatic semantic web service composition, where both QoS and quality of semantic match making will be optimised simultaneously. However, customers often prefer a service composition that matches their requirement most with highest QoS.

The overall goal of this paper is to \textit{develop an comprehensive quality-aware automated semantic web service composition that satisfactorily optimises both functional and non-functional requirements}. Particularly, this paper considers the quality of semantic matchmaking quality and QoS and two structural constructs (sequence and parallel) for building optimised composition solution using Particle Swarm Optimisation (PSO). We aim to provide a more applicable and adaptive way to measure semantic matchmaking in automated semantic web service composition. We will achieve three objectives in this work as follows:

\begin{enumerate}
 \item To propose a comprehensive quality model that address QoS and semantic matchmaking quality in considering different matching types associated with corresponding semantic similarity. This approach is consider to be a more applicable and adaptive way of finding an optimised solution in semantic web service composition.

 \item To propose a PSO-based service composition model that utilise the proposed quality model. In PSO, each particle represent a weighted graph sorts out an optimised service queue as an indirect representation of web service composition with the consideration of comprehensive quality, and this service queue is further decoded using a graph building algorithm to generate a final solution.

 \item To evaluate the performance of comprehensive quality awareness semantic web service composition by utilising benchmark datasets from Web Services Challenge 2009 (WSC09) \cite{kona2009wsc}.
\end{enumerate}

The remains of this paper are organized as the following: Sect. \ref{background} provides the background on the semantic web service composition, and related works; Sect. \ref{qswsc_approach} presents an overview of comprehensive quality awareness semantic automated web service composition consisting of comprehensive quality evaluation model and PSO-based service composition algorithm; Sect. \ref{experiment_design} describes the experiments conducted to test the effectiveness of proposed model; Sect. \ref{results_analysis} presents the results and analysis of the experiment; Sect. \ref{conclusion} is the paper conclusion.

@@

The purpose of web service composition is to accomplish an arbitrarily complex task fulfilling customer's requirement, which could be denoted as a composite goal: $Comp.G(F(T_{Input}, T_{Output}), NF(T_{QoS}))$. This overall composite goal is demonstrated in two parts. The first functional part is a given task input or input set to get the desired Task output or output set, it typically refers to users' functional requirement; another nonfunctional part specifies the acceptable level of composite quality of service. To accomplish the composite goal, two stages are involved: services discovery and service selection. Firstly, service discovery is to find matched web service: $S_{n}(F(S_{Input}, S_{Output}), NF(S_{QoS}))$ from Service Repository: $S \{S_{1}, S_{2},..., S_{n} \}$ with the given $T_{Input}$. Meanwhile, a output set is initialised and updated with found services output, which could be denoted as  $Output Set(T_{input}, S_{output} \in S_1,...,S_{output} \in S_{n-k})$. The Output Set is used to discovery all related services until the desired $T_{Output}$ found in the updated Output Set. The discovery process normally results in more than one solutions. Service selection is to select one of those composite solution considering the closest QoS to $T_{QoS}$. To ensure the composite solution returns exact the same or very close $T_{Output}$, we consider a comprehensive quality in both discovery and selection stages, where two challenges mentioned in Sect. \ref{introduction} are also addressed in Sect. \ref{qswsc_approach}.
